Knowledge discovery in networked systems

### 2015-07-29 paper.tex
All templates of novadelete have been input

\title{Declarative Data Analytic}
\author{}

@@

For example, if we would like to specify a component-level dependency: $vm_1
\rightarrow vm_2$, we need to make it clear what logs are instances of $vm_1$
and $vm_2$. To do this, a candidate specification would be ``machine\_name =
$vm_1$. This specification is still in the scope of \saf{}. Based on this, the
specification over the logs is similar to specification over the directory paths
in the file system.

@@

@@

\begin{itemize}
\item Backtracking the execution according to causality relationship
  \begin{itemize}
  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
  \item Convert the log in JSON into an SQLite3 database. (done)
  \item Obtain domain-specific knowledge about OpenStack and the execution:
    data/models(Filtered Message Sequence)
  \item Specify the domain-specific knowledge in SAF --- on different levels ---
    and found corresponding traces.
    \begin{itemize}
    \item Level 1: event dependency
    \item Level 2: component dependency
    \end{itemize}
  \item Build the causality graph for different levels.
  \end{itemize}
\item Root cause detection of failure symptoms based on the backtracking technique
\end{itemize}

>>>>

\title{Knowledge discovery in networked systems}
\author{}

@@

For example, if we would like to specify a component-level dependency: $vm_1
\rightarrow vm_2$, we need to make it clear what logs are instances of $vm_1$
and $vm_2$. To do this, a candidate specification would be ``machine\_name =
$vm_1$''. This specification is still in the scope of \saf{}. Based on this, the
specification over the logs is similar to specification over the directory paths
in the file system.

@@

\subsection{7/29}
\label{sec:meeting:729}

In today's meeting, we discussed about the case study of Openstack logs. Based
on the discussion, further steps were proposed to continue the project.

\paragraph{Todo}
\begin{itemize}
\item Finish the case study of novadelete.
\item Re-do the case study on novaboot.
\item Develop back-tracking and forward-tracking utilities:
  back-tracking(event\_seed, model) = matched part of the model.
\item Develop component-level behavior model.
\item Develop NFA-based specification of behavior models.
\end{itemize}

@@

\begin{itemize}
\item Use SAF to analyze Openstack logs.
  \begin{itemize}
  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
  \item Convert the log in JSON into an SQLite3 database. (done)
  \item Convert the log in JSON into an event sqlite3 database required by \saf{}.
    \begin{itemize}
    \item The schema of the database should satisfy the format of the event in
      \saf{}.

      As stated in ``SAF-trunk/plugins/p2db/eventattrs.c'' in p2db plugin of \saf{}: ``Each line of
      attribute is of the following format $\langle$attributename,
      attributetype$\rangle$ ... Each event specification must have the
      following attributes at a minimum "eventno integer", "eventtype text",
      "timestamp integer",	"timestampusec integer", "origin text" ''

      Bug: During the test of SAF, when the wildcard symbol---e.g.,
      port=\$1---is used in the behavior model, dependent events
      whose field values are 0 are not output by SAF. However, if the value of a
      field is explicitly designated as 0, dependent events will be correctly
      output.

      Fix: the problem lie in the file
      ``SAF-trunk/framework/common/sqlutils.py''. In line 76, SAF tests the
      validity of a value by ``if (newv):'', this causes the problem that when
      the value of a field is 0 in dependent events, it will not be
      processed. On the other hand, if the user explicitly specifies the value
      of the field as 0, SAF will convert the value into string ``0'', which
      is accepted by the conditional.
    \item The information extracted from JSON is of coarse granularity. Further
      parsing is needed to obtain detailed information, such as IP addresses,
      device ids.

    \item Sort the log information according to logs' timestamps. (The original
      log is already in the correct order)
    \end{itemize}

  \item Obtain domain-specific knowledge about OpenStack and the execution:
    data/models(Filtered Message Sequence)
  \item Specify the domain-specific knowledge in SAF --- on different levels ---
    and found corresponding traces.
    \begin{itemize}
    \item Level 1: event dependency
    \item Level 2: component dependency
    \end{itemize}
  \item Build the causality graph for different levels.
  \end{itemize}
\item Root cause detection of failure symptoms based on the backtracking technique
\end{itemize}
